Report and analysis on implementation of IMM algorithm for multiple-model dynamics tracking

### 2020-02-02 Latex/draft.tex
gdsgds

        \item blue : 1 sensors ON, happens only at the conrners of the grid

@@

@@

Being the agent's dynamic costantly switching between the models in the set choosen, a single kalman filter won't give us acceptable results while 

@@

memoryless random process $P\{s_{k+1}^{j}|s_{k}^{i}\}\pi_{ji}$ $\forall\ j,i$ and that the model set $\mathbbm{M}$ is the correct one and is time-invariant.

@@

 The design parameters of the IMM are the model set $\mathbbm{M}$, the process and measurement noise spectral density matrices $Q$ and $R$, the initial 
 state and covariance $\hat{x}_{0|0}$ and $P_{0|0}$ and the transition matrix $T$ containing all the $\pi_{ji}$.

@@

                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})']\mu_{k-1}^{j|i}

@@

        Here we take all the model probabilities computed at the previous step and mix them together with the 

@@

            &\\
            &\\
            &\\
            &\\
            &\\
            &\\

@@

@@

>>>>

        \item blue : 1 sensors ON

@@

    Note that the blue case happens only at the borders and corners of the grid.

@@

Being the agent's dynamic costantly switching between the models in the set chosen, a single kalman filter won't give us acceptable results while 

@@

memoryless random process $P\{s_{k+1}^{(j)}|s_{k}^{(j)}\}\pi_{ji}$ $\forall\ j,i$ and that the model set $\mathbbm{M}$ is the correct one and is time-invariant.

@@

 The design parameters of the IMM are the model set $\mathbbm{M}$, the process and measurement noise spectral density 
 matrices $Q$ and $R$ for each model and sensor, the initial state and covariance $\hat{x}_{0|0}$ and $P_{0|0}$ 
 and the transition matrix $T$ containing all the $\pi_{ji}$.

@@

                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}

@@

        Here we take all the output model probabilities computed at the previous iteration of the IMM and mix them together with the 

@@

            &\hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1})\\
            &P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1}\\
            &\bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})\\
            &S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}\\
            &W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}\\
            &\hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}\\
            &P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}

@@

            &L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})\\
            &\mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}

@@

         &\hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}\\
         &P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}
